### 2025-07-12 multiple-regression.qmd
20250712 - bootstrap regression

>>>>

Another approach to handling outliers is to use boostrapping, which involves fitting models to various bootstrap resamples of the data.
Bootstrap samples are datasets generated by sampling repeatedly with replacement.

We set up the bootstrap folds using the `bootstraps()` function of the `rsample` package [@R-sample].

```{r}
set.seed(52242)
bootstrapSamples <- 2000

# Create bootstrap resamples (with apparent = TRUE)
boots <- rsample::bootstraps(
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  times = bootstrapSamples,
  apparent = TRUE
)

# Define recipe
rec <- recipes::recipe(
  fantasyPoints_transformed ~ age + height + weight + target_share,
  data = player_stats_seasonal %>% filter(position %in% c("WR"))
) %>%
  recipes::step_log(target_share, offset = 1) # replace I(log(target_share + 1))

# Define model spec and workflow
lm_spec <- parsnip::linear_reg() %>%
  parsnip::set_engine("lm") %>%
  parsnip::set_mode("regression")

lm_workflow <- workflows::workflow() %>%
  workflows::add_recipe(rec) %>%
  workflows::add_model(lm_spec)

# Function for fitting the models on the bootstrap samples
fit_lm <- function(split) {
  analysis_data <- rsample::analysis(split)
  fit <- workflows::fit(lm_workflow, data = analysis_data)
  broom::tidy(fit)
}

# Fit bootstrap models and save results
boot_models <- boots %>%
  mutate(coef_info = purrr::map(splits, fit_lm))

# Extract bootstrapped coefficients
boot_coefs <- 
  boot_models %>% 
  tidyr::unnest(coef_info)

# Compute percentile intervals for the regression coefficients
percentile_intervals <- rsample::int_pctl(boot_models, coef_info)
#percentile_intervals <- rsample::int_pctl(boot_results, results)

percentile_intervals
```

```{r}
#| label: fig-miDensityPlot
#| fig-cap: "Histogram of Parameter Estimates Across Bootstraps."
#| fig-alt: "Histogram of Parameter Estimates Across Bootstraps."

ggplot(
  boot_coefs,
  aes(estimate)) +
  geom_histogram(
    fill = "gray80",
    color = "black") +
  facet_wrap(
    ~ term,
    scales = "free") +
  geom_vline(
    aes(
      xintercept = .lower),
    data = percentile_intervals,
    col = "blue",
    linetype = "dashed") +
  geom_vline(
    aes(
      xintercept = .upper),
    data = percentile_intervals,
    col = "blue",
    linetype = "dashed") +
  labs(
    title = "Bootstrap Distributions of Coefficients",
    x = "Coefficient Estimate",
    y = "Count") +
  theme_classic()
```
